### 2023-04-06 main.tex
i

\textbf{Remark}: using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as {\color{red}{add (-1)}}
	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(y_{k},c_{k},\ldots,c_{m})

@@

		\langle n_{s_{1}}^{y_{1}},\ldots, n_{s_{m}}^{y_{m}}\rangle_{\text{stat}}&

@@

This probability \eqref{Prob-m} can be seen as the component \eqref{steadyStateH-coeff} of the stationary state \eqref{steadyStateH} of a chain of length $m$ with each coordinates $y_{i}$ occupied by $s_{x}\neq 1$, i.e. 

@@

	\Psi_{\bm{y}}(s_{1},\ldots,s_{m})=\widehat{\Psi}_{\bm{y}}(s_{1},\ldots,s_{m})
Thus, by applying the formula \eqref{ABS_intermediate} we have 
	\widehat{\Psi}_{\bm{y}}(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
By using the relation \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we have the equations for arbitrary correlations.

@@

@@

	\langle n_{s_{1}}^{x} n_{s_{2}}^{y}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})

@@

\begin{equation}\label{three-pts-corr}
        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\prod_{k=1}^{3}\beta_{s_{k}}+\sum_{k=1}^{3}\frac{(L-y_{k})}{(L+1)}(\alpha_{s_{k}}-\beta_{s_{k}})\prod_{q=1\,:\,q\neq k}^{3}\beta_{s_{q}}

@@

@@

        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}\prod_{k=1}^{3}(\alpha_{s_{k}}-\beta_{s_{k}})
\textbf{Remark}: the one and two points correlations computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 

>>>>

\textbf{Remark}: using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as 
f(c_{1},\ldots,c_{m})f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\sum_{t_{m}=1}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(y_{q},c_{q},\ldots,c_{m})
%\begin{equation}
%	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(y_{k},c_{k},\ldots,c_{m})
%\end{equation}

@@

		\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{\text{stat}}&

@@

This probability \eqref{Prob-m} $\Psi(\bm{s})$ of a chain of length $m$ with each coordinates $y_{i}$ occupied by $s_{x}\neq 1$, i.e. 

@@

	\Psi_{\bm{y}}(s_{1},\ldots,s_{m})=\Psi^{'}_{\bm{y}}(s_{1},\ldots,s_{m})
Thus, by applying \eqref{ABS_intermediate} we have 
	\Psi_{\bm{y}}(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
Introducing $f(c_{1},\ldots,c_{m})$ and $g_{a}(y_{a},c_{a},\ldots,c_{m})$ we have the formulas for arbitrary correlations.

@@

	\langle n_{s_{1}}^{x} n_{s_{2}}^{y}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
Therefore, we obtain the second cumulant, i.e. the second truncated correlation as 

@@

		\mathbb{E}[n_{y_{1}}^{s_{1}}n_{y_{2}}^{s_{2}}]-\mathbb{E}[n_{y_{1}}^{s_{1}}]\mathbb{E}[n_{y_{2}}^{s_{2}}]=-\frac{y_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)

@@

\begin{align}\label{three-pts-corr}
        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}
        \\&+\nonumber
        \frac{(L-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}
        \\&+\nonumber

@@

        \\&+\nonumber

@@

        \\&+\nonumber
        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 
